\documentclass{article}

\usepackage[margin=1in]{geometry}

\usepackage{multicol}

\usepackage{tabto}

\usepackage[ampersand]{easylist}
  \newcommand\titlebullets{
    \ListProperties(Style1**=\bfseries,Style1*= ,Style2*=$\bullet$ )
  }
  \newcommand\titleparagraph{
    \ListProperties(Style1**=\bfseries,Style*= )
  }

\usepackage{titlesec}
  \titleformat{\section}
    {\Large\bfseries}{\thesection}{1em}{}[{\titlerule[0.8pt]}]



\begin{document}
  \pagenumbering{gobble}
  \begin{easylist}[itemize]\end{easylist} % stop list numbering

  \begin{center}
    \Huge \textbf{Richard Sun}\\[1ex]
    \large
    richardsun29@ucla.edu $\bullet$
    (619) 621-1012 $\bullet$
    github.com/richardsun29
  \end{center}


  \section*{Education}

      \textbf{University of California, Los Angeles}
      \hfill Expected Graduation: June 2018\\
      Computer Science, BS\\
      GPA: 3.9


  \section*{Work Experience}

    \begin{easylist} \titleparagraph
      & Software Development Intern
          \textnormal{$|$ Symantec \hfill June 2016 - Nov 2016,
                                          June 2017 - Sept 2017}
        && Worked on SONAR, a C++ Windows driver that provides heuristic
           antivirus protection
        && Developed a proof-of-concept feature which successfully detected a
           new ransomware sample

      & Development Lead \& IT
          \textnormal{$|$ UCLA Student Media \hfill May 2015 - Present}
        && Full stack development using Django, AngularJS, Ionic, React Native
        && Manage servers and Digital Ocean droplets that run over 10 websites

    \end{easylist}


  \section*{Projects}

    \begin{easylist} \titleparagraph

      & UCLA Maps
        && Led development on a Django backend that does outdoor and indoor
           navigation in UCLA. We developed an indoor navigation library that
           can draw routes from GIS data.
        && Worked on the React Native frontend to help implement more robust
           asynchronous code.

      & AppGet
        && A PaaS application designed to allow users to create and deploy
           mobile apps in minutes, without writing any code. We provide fully
           functional components that clients can customize through a web
           interface. We used AngularJS and the Ionic Framework to make use of
           their templating system.

%      & Class Scanner
%        && Python program that checks for open seats in a class. It parses a
%           HTML page using BeautifulSoup and sends notifications on Slack.

%      & Tetris
%        && Created Tetris from scratch using Unity and C\#. This project
%           helped me understand object-oriented and event-driven programming
%           better.

      & Robocode Workshop
        && Hosted a workshop for ACM on Robocode, a Java robot battle
           simulator. Demonstrated a simple robot that predicted enemy movement
           to dodge bullets.

    \end{easylist}


  \section*{Coursework}

    \vspace{-2.5ex}
    \begin{multicols}{2}
      \begin{easylist}[itemize]
        & Software Engineering
        & Operating Systems
        & Databases
        & Programming Languages
        & Networking
        & Data Structures and Algorithms
      \end{easylist}
    \end{multicols}


  \section*{Skills}

    \vspace{-2.5ex}
    \begin{multicols}{2}
      \begin{easylist} \titlebullets
        & Languages
          && C++                    \tab $\bullet$ C
          && Python                 \tab $\bullet$ Javascript

        \columnbreak

        & Tools
          && MySQL, Django          \tab $\bullet$ Linux
          && AngularJS, React       \tab $\bullet$ Git

      \end{easylist}
    \end{multicols}

\end{document}
